Turnover of species and interactions

### 2018-10-26 paper/data-exploration/turnover.Rmd
Add thresholds to form focal species

species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(sp_name) %>% 
  plot_freq_step() +
  labs(title = "number of locations per species", 
       subtitle = "species turnover in the Web of Life database")

# species_list %>%
#   remove_unknown_species() %>% 
#   get_sp_freq_by_group(genus) %>%
#   plot_freq_step()+
#   ggtitle("number of locations per genus")
```

```{r}
species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(sp_name) %>%
  dplyr::filter(n_loc_rank <= 10) %>%
  dplyr::select(n_loc_rank, guild, sp_name, n_loc) %>%
  dplyr::arrange(guild, n_loc_rank) %>%
  knitr::kable(col.names = c("", "guild", "species", "# locations"))
```

@@

interaction_list %>%
  remove_unknown_species() %>% 
  get_int_freq_by_group(pla_name, pol_name) %>% 
  plot_freq_step() +
  labs(title = "locations per interactions", 
       subtitle = "interactions turnover in the Web of Life database")
# 
# interaction_list %>% 
#   remove_unknown_species() %>% 
#   get_int_freq_by_group(pla_genus, pol_genus) %>% 
#   plot_freq_step() +
#   ggtitle("locations per interactions (genus)")
```

>>>>

sp_rank <- species_list %>%
  remove_unknown_species() %>% 
  get_sp_freq_by_group(sp_name)

sp_rank %>%
  plot_freq_step() +
  geom_hline(yintercept = 4.5, size = 0.5, linetype = 2) +
  labs(title = "number of locations per species", 
       subtitle = "species turnover in the Web of Life database", 
       caption = "dashed line indicates the (arbitrary) threshold for selecting focal species")

```

```{r}
sp_rank %>% 
  dplyr::filter(n_loc_rank <= 10) %>%
  dplyr::select(n_loc_rank, guild, sp_name, n_loc) %>%
  dplyr::arrange(guild, n_loc_rank) %>%
  knitr::kable(col.names = c("", "guild", "species", "# locations"))
```

@@

int_rank <- interaction_list %>%
  remove_unknown_species() %>% 
  get_int_freq_by_group(pla_name, pol_name)

int_rank %>%
  plot_freq_step() +
  geom_hline(yintercept = 2.9, size = 0.5, linetype = 2) +
  labs(title = "locations per interactions", 
       subtitle = "interactions turnover in the Web of Life database", 
       caption = "dashed line indicates the (arbitrary) threshold for selecting focal species")
```
